---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# assignmentb2.graphHistograms

<!-- badges: start -->
<!-- badges: end -->

The goal of assignmentb2.graphHistograms is to provide users with an efficient way of graphing histograms when doing data exploration, to speed up the process of a common practice done when understanding what the data in a dataset looks like. A common use is when you are wanting to understand the distribution and patterns of a variable in a dataset, to determine what type of distribution, what trends are present, and whether this fits a question you have in mind. The specific use of this package is to plot a histogram of a numerical variable in the dataset of choosing, and label it's mean value on the plot. It also outputs what the mean is so that this can be documented instead of relying on the graph. 

## Installation

You can install the development version of assignmentb2.graphHistograms from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2025/assignmentb2.graphHistograms", ref = "0.1.0")
```

## Examples

This is a basic example which shows you how to solve a common problem:

```{r example}
library(assignmentb2.graphHistograms)
plot_distribution_and_mean(mtcars, mpg, 10, 4)
```

```{r example_2}
plot_distribution_and_mean(mtcars, wt)
```

## Dependencies

This package requires certain dependencies, which are loaded upon download. For reference, the packages are listed below:

```{r}
library(dplyr)
library(ggplot2)
library(magrittr)
library(assignmentb2.graphHistograms) # this package!
```
